---
title: "Getting started"
author: "Andreas M. Brandmaier"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```

## R Markdown

Load the library.

```{r lib}
library(pdcsync)
```

Simulate two time series. The first time series is generated from an autoregressive process. 
The second time series is a time-shifted version of the first one with some added minimal noise.
There is an induced complete break of symmetry between time points 200 and 400.

```{r ar}
N <- 1000

t1 <- arima.sim(model = list(ar = 0.2), n = N)

# t2 is later than t1; t1 leads
t2 <- c(t1[4:(length(t1))], 0, 0, 0) + rnorm(N, 0, 0.001)

# no synchrony between 200 and 400
t2[200:400] <- runif(201, 0, 1)
```

Call the synchronization detection:

```{r pdcsync}
sync <- pdcsync(t1, t2)
```

Plot the synchronization profile

```{r plot}
plot(sync)
```

Plot the synchronization profile using the extended plot method:

```{r plot2}
syncplot(sync)

```

Compute an (experimental) global synchronisation measure (between 0 and 1, with higher values indicating stronger synchrony). 

```{r}
averageAggregatedSynchrony(sync)
```

Now, we further reduce the synchronisation and re-run the algorithm again.

```{r}
# no synchrony between 200 and 400
t2[200:600] <- runif(201, 0, 1)
sync <- pdcsync(t1, t2)
```



Plot the synchronization profile using the extended plot method:

```{r plot2b}
syncplot(sync)

```

Compute an (experimental) global synchronisation measure (between 0 and 1, with higher values indicating stronger synchrony). This value is lower than before because global synchronisation decreased.

```{r}
averageAggregatedSynchrony(sync)
```